Software Citation Principles

### 2016-07-24 sc-principles/software-citation-principles.tex
comment in B.7

This case describes the need for a research who has contributed to software (by design, software engineering, development, testing, patching, documentation, training, evangelizing, etc.)
to have their software work recognized by their employer or colleagues for the purpose of career advancement and increased professional reputation.

@@

This case describes the need for a research who has contributed to software (by design, software engineering, development, testing, patching, documentation, training, evangelizing, etc.) to have their software work recognized by their employer or colleagues for the purpose of career advancement and increased professional reputation.

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}
\niemnote{the title and description are quite different---based on the description, this actually seems like 5}

>>>>

This case describes the need for a researcher who has contributed to software (by design, software engineering, development, testing, patching, documentation, training, evangelizing, etc.)
to have their software work recognized by their employer or colleagues for the purpose of career advancement and increased professional reputation.

@@

This case describes the need for a researcher who has contributed to software (by design, software engineering, development, testing, patching, documentation, training, evangelizing, etc.) to have their software work recognized by their employer or colleagues for the purpose of career advancement and increased professional reputation.

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}
\niemnote{the title and description are quite different---based on the description, this actually seems like 5} \katznote{somehow, the description is the same was copied from 5's - not sure why/how - but I don't think this matches the title at all.  The title matches 1.  It's a case of a researcher using someone else's software for a paper.  Unlike 1, which is general in terms of the use, likely a new science results, here the use of a benchmarking study, but again, the outcome is a paper that needs to cite the software.  I'm fairly confident we can delete this one entirely, as it is really subsumed within 1.  If we do this, we should do it in the google doc too.}
